---
title: "Work"
---
---------------------------------------
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

```{r}
library(vembedr)
```

### <u>Publications</u>

**Pharmacoepidemiology & Drug Safety** (June 2019)  
<a href="https://doi.org/10.1002/pds.4807">*A simulation study of the statistical power and signaling characteristics of an early season sequential test for influenza vaccine safety.*</a> 

**The Journal of Infectious Diseases** (November 2020)  
<a href="https://doi.org/10.1093/infdis/jiaa543">*Guillain-Barré Syndrome After High-Dose Influenza Vaccine Administration in the United States, 2018–2019 Season.*</a> 

<br>

### <u>Work in progress</u>

**Apascaritei, P., Radl, J. & Swarr, M. (2023).**  
<a href="https://e-archivo.uc3m.es/entities/publication/cd85f716-44aa-4fd8-9d7d-7707fce16ff4">*Material incentives drive gender differences in cognitive effort among children.*</a>  

**Radl, J., Apascaratei, P., Foley, W., Kröger, L., Lorente, P.,  Palacios-Abad, A., Solga, H., Stuhler, J., & Swarr, M. (2024).**  
<a href="https://e-archivo.uc3m.es/entities/publication/6a1cd05f-6849-45d3-b1fd-52fdc9e09fe0">*How socioeconomic status shapes cognitive effort: A laboratory study among fifth graders.*</a>  

<br>

### <u>Presentations</u>

**"Effort and Social Equality" ECSR Thematic Conference** (June 2023)  
<a href="https://youtu.be/kkl-3iRxezs?si=unubnITj7J2767kM&t=2235" width = "80%">*Material incentives drive gender differences in cognitive effort among children.*</a>

```{r}
embed_url("https://youtu.be/kkl-3iRxezs?si=unubnITj7J2767kM&t=2235")
```

<br>

### <u>Master's thesis</u>
**MSc in Economic Development and Growth -- UC3M (2022)**  
*Co-ethnic density and economic outcomes: A microeconometric analysis of how residential settlement patterns impact immigrant wages using the Spanish National Survey of Immigrants*  

<iframe
    src="files/Swarr_Madeline_MEDEG_Thesis_final_final.pdf"
    width="100%"
    height="900px"
></iframe>
